Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"

### 2016-11-16 1047_supp.tex
s

\section{More Denoising Results on the 60 Cropped Real Noisy Images from \cite{crosschannel2016}}
In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

>>>>

\section{More Denoising Results on the 60 Cropped Real Noisy Images from \cite{crosschannel2016}}
In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped from \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
